Thermonuclear burst model-observation comparisons with {\sc concord}

### 2018-03-19 doc/ms.tex
Created function calc_mr for mass, radius from g, 1+z

@@

>>>>

Here we explore the ways that host system  parameters affect the observed properties of thermonuclear bursts, and assess to what degree these effects can be corrected for.
%
In \S\ref{sec:data} we describe the typical characteristics of burst observations along with those properties that can be predicted by numerical models.
% 
In \S\ref{sec:analysis} we explore a number of methods to infer properties of the bursting source, and assess their accuracy.
%
In \S\ref{sec:simulations} we apply these methods to a range of simulated data to assess what degree of systematic errors these measurements might be subject to.

@@

\section{Application to simulated data} 
\label{sec:simulations}

Here we assemble and analyse a number of datasets to assess the precision and accuracy of the approaches described in the previous section.
